Paper analysis

### 2025-04-01 Paper_analysis.Rmd
update again

```{r shap_pol, fig.width=9}
grid.arrange(
  sv_importance(ex.polbase.glb) + egg::theme_article(),
  sv_importance(ex.polmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

grid.arrange(
  polbase.ntr_pland.pdp$plot() + ggtitle("ntr_pland PDP"),
  polbase.ntr_pland.ale$plot() + ggtitle("ntr_pland ALE"),

  polbase.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland PDP"),
  polbase.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland ALE"),
  ncol = 2
)

@@

```{r shap_pol_margshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.polmarg.glb, v="ntr_pland") + egg::theme_article(),
  sv_dependence(ex.polmarg.glb, v="ann_agr_pland") + egg::theme_article()
)

@@

grid.arrange(
  polmarg.ntr_pland.pdp$plot() + ggtitle("ntr_pland PDP"),
  polmarg.ntr_pland.ale$plot() + ggtitle("ntr_pland ALE"),

  polmarg.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland PDP"),
  polmarg.ann_agr_pland.ale$plot() + ggtitle("ann_agr_pland ALE"),
  ncol = 2
)

@@

grid.arrange(
  sv_importance(ex.nexpbase.glb) + egg::theme_article(), 
  sv_importance(ex.nexpmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

grid.arrange(
  sv_dependence(ex.nexpbase.glb, v="ntr_pland") + egg::theme_article(),
  sv_dependence(ex.nexpbase.glb, v="ann_agr_pland") + egg::theme_article(), 
  sv_dependence(ex.nexpbase.glb, v="ntr_ed") + egg::theme_article(), 
  ncol = 2
)

@@

grid.arrange(
  nexpbase.ntr_pland.pdp$plot() + ggtitle("ntr_pland PDP"),
  nexpbase.ntr_pland.ale$plot() + ggtitle("ntr_pland ALE"),

  nexpbase.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland PDP"),
  nexpbase.ann_agr_pland.ale$plot() + ggtitle("ann_agr_pland ALE"),

  nexpbase.ntr_ed.pdp$plot() + ggtitle("ntr_ed PDP"),
  nexpbase.ntr_ed.ale$plot() + ggtitle("ntr_ed ALE"),
  ncol = 2
)

@@

```{r shap_nexp_margshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.nexpmarg.glb, v="ntr_pland") + egg::theme_article(),
  sv_dependence(ex.nexpmarg.glb, v="ann_agr_pland") + egg::theme_article(), 
  sv_dependence(ex.nexpmarg.glb, v="ntr_ed") + egg::theme_article(), 
  ncol = 2
)

@@

grid.arrange(
  nexpmarg.ntr_pland.pdp$plot() + ggtitle("ntr_pland PDP"),
  nexpmarg.ntr_pland.ale$plot() + ggtitle("ntr_pland ALE"),

  nexpmarg.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland PDP"),
  nexpmarg.ann_agr_pland.ale$plot() + ggtitle("ann_agr_pland ALE"),

  nexpmarg.ntr_ed.pdp$plot() + ggtitle("ntr_ed PDP"),
  nexpmarg.ntr_ed.ale$plot() + ggtitle("ntr_ed ALE"),
  ncol = 2
)

@@

```{r shap_sed, fig.width=9}
grid.arrange(
  sv_importance(ex.sedbase.glb) + egg::theme_article(),
  sv_importance(ex.sedmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

```{r shap_sed_baseshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.sedbase.glb, v="ann_agr_ed") + egg::theme_article()
)

@@

grid.arrange(
  sedbase.ann_agr_ed.pdp$plot() + ggtitle("ann_agr_ed PDP") +
    egg::theme_article(),
  sedbase.ann_agr_ed.ale$plot() + ggtitle("ann_agr_ed ALE") +
    egg::theme_article(),

  ncol = 2
)

@@

```{r shap_sed_margshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.sedmarg.glb, v="ann_agr_ed") + egg::theme_article(),
  sv_dependence(ex.sedmarg.glb, v="field_frac_mn") + egg::theme_article(),
  ncol=2
)

@@

grid.arrange(
  sedmarg.ann_agr_ed.pdp$plot() + ggtitle("ann_agr_ed PDP") +
    egg::theme_article(),
  sedmarg.ann_agr_ed.ale$plot() + ggtitle("ann_agr_ed ALE") +
    egg::theme_article(),

@@

  ncol = 2
)

@@

```{r shap_qb, fig.width=9}
grid.arrange(
  sv_importance(ex.qbbase.glb) + egg::theme_article(),
  sv_importance(ex.qbmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

```{r shap_qb_baseshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.qbbase.glb, v="field_frac_mn") + egg::theme_article()
)

@@

@@

grid.arrange(
  qbbase.field_frac_mn.pdp$plot() + ggtitle("field_frac_mn PDP") +
    egg::theme_article(),
  sedbase.field_frac_mn.ale$plot() + ggtitle("field_frac_mn ALE") +
    egg::theme_article(),

  ncol = 2
)

@@

```{r shap_qb_margshap, fig.width=9}
grid.arrange(
  sv_dependence(ex.qbmarg.glb, v="ann_agr_cohesion") + egg::theme_article(),
  sv_dependence(ex.qbmarg.glb, v="prn_pagr") + egg::theme_article(),
  sv_dependence(ex.qbmarg.glb, v="prn_agr_para_mn") + egg::theme_article(),
  ncol=2
)

@@

grid.arrange(
  qbmarg.ann_agr_cohesion.pdp$plot() + ggtitle("ann_agr_cohesion PDP") +
    egg::theme_article(),
  qbmarg.ann_agr_cohesion.ale$plot() + ggtitle("ann_agr_cohesion ALE") +
    egg::theme_article(),

  qbmarg.prn_pagr.pdp$plot() + ggtitle("prn_pagr PDP") +
    egg::theme_article(),
  qbmarg.prn_pagr.ale$plot() + ggtitle("prn_pagr ALE") +
    egg::theme_article(),

  qbmarg.prn_agr_para_mn.pdp$plot() + ggtitle("prn_agr_para_mn PDP") +
    egg::theme_article(),
  qbmarg.prn_agr_para_mn.ale$plot() + ggtitle("prn_agr_para_mn ALE") +
    egg::theme_article(),

  ncol = 2
)

@@

# psych::pairs.panels(dat.selectedvar)

>>>>

```{r shap_pol, fig.width=9}
cowplot::plot_grid(
  sv_importance(ex.polbase.glb) + egg::theme_article(),
  sv_importance(ex.polmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

cowplot::plot_grid(
  polbase.ntr_pland.pdp$plot() + ggtitle("ntr_pland PDP") + egg::theme_article(),
  polbase.ntr_pland.ale$plot() + ggtitle("ntr_pland ALE") + egg::theme_article(),

  polbase.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland PDP") + egg::theme_article(),
  polbase.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland ALE") + egg::theme_article(),
  ncol = 2, align = "v"
)

@@

```{r shap_pol_margshap, fig.width=9}
cowplot::plot_grid(
  sv_dependence(ex.polmarg.glb, v="ntr_pland") + egg::theme_article(),
  sv_dependence(ex.polmarg.glb, v="ann_agr_pland") + egg::theme_article(),
  ncol = 2, align = "v"
)

@@

cowplot::plot_grid(
  polmarg.ntr_pland.pdp$plot() + ggtitle("ntr_pland PDP") + egg::theme_article(),
  polmarg.ntr_pland.ale$plot() + ggtitle("ntr_pland ALE") + egg::theme_article(),

  polmarg.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland PDP") + egg::theme_article(),
  polmarg.ann_agr_pland.ale$plot() + ggtitle("ann_agr_pland ALE") + egg::theme_article(),
  ncol = 2, align = "v"
)

@@

cowplot::plot_grid(
  sv_importance(ex.nexpbase.glb) + egg::theme_article(), 
  sv_importance(ex.nexpmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

cowplot::plot_grid(
  sv_dependence(ex.nexpbase.glb, v="ntr_pland") + egg::theme_article(),
  sv_dependence(ex.nexpbase.glb, v="ann_agr_pland") + egg::theme_article(), 
  sv_dependence(ex.nexpbase.glb, v="ntr_ed") + egg::theme_article(), 
  ncol = 2, align = "v"
)

@@

cowplot::plot_grid(
  nexpbase.ntr_pland.pdp$plot() + ggtitle("ntr_pland PDP") + egg::theme_article(),
  nexpbase.ntr_pland.ale$plot() + ggtitle("ntr_pland ALE") + egg::theme_article(),

  nexpbase.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland PDP") + egg::theme_article(),
  nexpbase.ann_agr_pland.ale$plot() + ggtitle("ann_agr_pland ALE") + egg::theme_article(),

  nexpbase.ntr_ed.pdp$plot() + ggtitle("ntr_ed PDP") + egg::theme_article(),
  nexpbase.ntr_ed.ale$plot() + ggtitle("ntr_ed ALE") + egg::theme_article(),
  ncol = 2, align = "v"
)

@@

```{r shap_nexp_margshap, fig.width=9}
cowplot::plot_grid(
  sv_dependence(ex.nexpmarg.glb, v="ntr_pland") + egg::theme_article(),
  sv_dependence(ex.nexpmarg.glb, v="ann_agr_pland") + egg::theme_article(), 
  sv_dependence(ex.nexpmarg.glb, v="ntr_ed") + egg::theme_article(), 
  ncol = 2, align = "v"
)

@@

cowplot::plot_grid(
  nexpmarg.ntr_pland.pdp$plot() + ggtitle("ntr_pland PDP") + egg::theme_article(),
  nexpmarg.ntr_pland.ale$plot() + ggtitle("ntr_pland ALE") + egg::theme_article(),

  nexpmarg.ann_agr_pland.pdp$plot() + ggtitle("ann_agr_pland PDP") + egg::theme_article(),
  nexpmarg.ann_agr_pland.ale$plot() + ggtitle("ann_agr_pland ALE") + egg::theme_article(),

  nexpmarg.ntr_ed.pdp$plot() + ggtitle("ntr_ed PDP") + egg::theme_article(),
  nexpmarg.ntr_ed.ale$plot() + ggtitle("ntr_ed ALE") + egg::theme_article(),
  ncol = 2, align = "v"
)

@@

```{r shap_sed, fig.width=9}
cowplot::plot_grid(
  sv_importance(ex.sedbase.glb) + egg::theme_article(),
  sv_importance(ex.sedmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

```{r shap_sed_baseshap, fig.width=9}
sv_dependence(ex.sedbase.glb, v="ann_agr_ed") + egg::theme_article()

@@

cowplot::plot_grid(
  sedbase.ann_agr_ed.pdp$plot() + ggtitle("ann_agr_ed PDP") +
    egg::theme_article(),
  sedbase.ann_agr_ed.ale$plot() + ggtitle("ann_agr_ed ALE") +
    egg::theme_article(),

  ncol = 2, align = "v"
)

@@

```{r shap_sed_margshap, fig.width=9}
cowplot::plot_grid(
  sv_dependence(ex.sedmarg.glb, v="ann_agr_ed") + egg::theme_article(),
  sv_dependence(ex.sedmarg.glb, v="field_frac_mn") + egg::theme_article(),
  ncol=2, align = "v"
)

@@

cowplot::plot_grid(
  sedmarg.ann_agr_ed.pdp$plot() + ggtitle("ann_agr_ed PDP") +
    egg::theme_article(),
  sedmarg.ann_agr_ed.ale$plot() + ggtitle("ann_agr_ed ALE") +
    egg::theme_article(),

@@

  ncol = 2, align = "v"
)

@@

```{r shap_qb, fig.width=9}
cowplot::plot_grid(
  sv_importance(ex.qbbase.glb) + egg::theme_article(),
  sv_importance(ex.qbmarg.glb) + egg::theme_article(),
  ncol = 2
)

@@

```{r shap_qb_baseshap, fig.width=9}
cowplot::plot_grid(
  sv_dependence(ex.qbbase.glb, v="ann_agr_cohesion") + egg::theme_article(),
  sv_dependence(ex.qbbase.glb, v="field_frac_mn") + egg::theme_article(),
  ncol = 2, align = "v"
)

@@

qbbase.ann_agr_cohesion.pdp = FeatureEffect$new(pred.qb_base, 
                                             feature = "ann_agr_cohesion",
                                             method = "pdp")

sedbase.ann_agr_cohesion.ale = FeatureEffect$new(pred.qb_base, 
                                              feature = "ann_agr_cohesion",
                                              method = "ale")

@@

cowplot::plot_grid(
  qbbase.ann_agr_cohesion.pdp$plot() + ggtitle("ann_agr_cohesion PDP") +
    egg::theme_article(),
  sedbase.ann_agr_cohesion.ale$plot() + ggtitle("ann_agr_cohesion ALE") +
    egg::theme_article(),

  qbbase.field_frac_mn.pdp$plot() + ggtitle("field_frac_mn PDP") +
    egg::theme_article(),
  sedbase.field_frac_mn.ale$plot() + ggtitle("field_frac_mn ALE") +
    egg::theme_article(),

  ncol = 2, align = "v"
)

@@

```{r shap_qb_margshap, fig.width=9}
cowplot::plot_grid(
  sv_dependence(ex.qbmarg.glb, v="ann_agr_cohesion") + egg::theme_article(),
  sv_dependence(ex.qbmarg.glb, v="prn_pagr") + egg::theme_article(),
  sv_dependence(ex.qbmarg.glb, v="prn_agr_para_mn") + egg::theme_article(),
  ncol=2, align = "v"
)

@@

cowplot::plot_grid(
  qbmarg.ann_agr_cohesion.pdp$plot() + ggtitle("ann_agr_cohesion PDP") + ylab("PDP") +
    egg::theme_article(),
  qbmarg.ann_agr_cohesion.ale$plot() + ggtitle("ann_agr_cohesion ALE") + ylab("ALE") +
    egg::theme_article(),

  qbmarg.prn_pagr.pdp$plot() + ggtitle("prn_pagr PDP") + ylab("PDP") +
    egg::theme_article(),
  qbmarg.prn_pagr.ale$plot() + ggtitle("prn_pagr ALE") + ylab("ALE") +
    egg::theme_article(),

  qbmarg.prn_agr_para_mn.pdp$plot() + ggtitle("prn_agr_para_mn PDP") + ylab("PDP") +
    egg::theme_article(),
  qbmarg.prn_agr_para_mn.ale$plot() + ggtitle("prn_agr_para_mn ALE") + ylab("ALE") +
    egg::theme_article(),

  ncol = 2, align = "v"
)

#### Correlation of important variables

dat.selectedvar <- dat %>% select(selectedvar)
psych::pairs.panels(dat.selectedvar)

@@
